Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-24 products/manuscript/Manuscript.qmd
IMG

**Table 5: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Build a normalized, forward‐slash path and include the image
or_u25_path <- normalizePath(
  here::here(
    "Images",
    "Adjusted OR for Adverse Birth Outcomes Women  less 25 Years.png"
  ),
  winslash = "/"
)
knitr::include_graphics(or_u25_path)

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Construct an absolute, forward‐slash path and include the image
fig3_path <- normalizePath(
  here::here(
    "Images",
    "Figure 3. Predicted Probability of Adverse Outcome by Gravidity Age  25.png"
  ),
  winslash = "/"
)
knitr::include_graphics(fig3_path)

>>>>

**Table 5: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  here::here("Images", "Adjusted ratio   less 25 Years.png")
)

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  here::here("Images", "Figure 3. Predicted Probability.png")
)
